Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-19 latex/article.tex
figs

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to refine cells
within the camera frustrum. When rendering a mesh, a key stage is the
rasterization one which digitizes triangles projected onto the
screen. As a consequence, having several triangles whose projections
lie inside the same pixel is something we should prevent. Hence,
distance criterion can be set in order to both control the geometrical
approximation and to ensure that cells project onto more than one
pixel. Figure \ref{fig_lod_octree} illustrates the level of details
(LoD for short criterion) we use.

\begin{figure}
  \begin{center}
    \includegraphics[width=0.4\linewidth]{viewlod2_small}  
  \end{center}
  \caption{Adaptive meshing in dimension 2 using the LoD distance and
    angular criterion.}
  \label{fig_lod_octree} 
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.9\textwidth]{figs/pipeline}
  \caption{ This figure summarizes our GPU pipeline. Data buffers are
    represented in green and computations in red. Each computation
    retrieves data from a buffer and fills a new one. }
  \label{fig_pipeline} 
\end{figure}

\begin{figure}
\centering
\includegraphics[height=0.2\textheight]{subdivision}
\caption{The octree at frame $t$ is stored as a list of Morton codes in a buffer. 
To update the tree, we fill a new buffer representing its state at frame $t+1$. 
On the GPU, each code of the first buffer is processed in parallel. 
If the cell is to be subdivided, it writes the codes of its children in the new buffer. 
If it merges, it writes either nothing, or the code of its parent (if it is the first child).
If it is kept, it just re-writes its own code. }
\label{subdivision}
\end{figure}

>>>>

As illustrated in Figure
\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
dependent criterion to decide if a cell needs to be refined: the
closer we are to the camera, the finer the cells are. In addition to
the distance criterion, we define an angular criterion to refine cells
within the camera frustrum. When rendering a mesh, a key stage is the
rasterization one which digitizes triangles projected onto the
screen. As a consequence, having several triangles whose projections
lie inside the same pixel is something we should prevent. Hence,
distance criterion can be set in order to both control the geometrical
approximation and to ensure that cells project onto more than one
pixel. Figure \ref{fig_lod_octree} illustrates the level of details
(LoD for short criterion) we use. More precisely, in dimension 2, if
$\alpha$ denotes the viewing angle, an object at distance $d$ from the
camera with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is
projected into more than one pixel (see
Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance criterion is based
on the ratio (\emph{visibility ratio} in the following)between the
cell diameter $l(c)$ (power of 2 depending on the depth), and $2\cdot
d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
center and the camera. For a given cell $c$, split and merge decision
are based on this visibility ratio:
\begin{itemize}
\item $c$ is split if its children cells have a visibility ratio
  greater than  constant $k$\,;
\item $c$ and its sibling cells are merged if their parent cell $c'$
  have av visibility ration lower than $k$\;
\item otherwise, the cell $c$ stays.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=4cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=4cm]{viewlod2_small}~~~~~
    \includegraphics[width=3.5cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
    angular criterion \emph{(middle)}. Based on LoD criterion
    evaluation, the cell buffer is
  updated between each frame \emph{(right)}.}
  \label{fig_lod_octree} 
\end{figure}
%
In addition to the distance criterion, we add an angular term in order
to prevent subdivision of cells far from the camera frustrum (see
Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
details but please not that stay, split and merge decisions of all cells are computed in
parallel from all cell morton codes.

Once decisions have been made, a new set of cells are sent to the mesh
generation step described above. Updating the cell buffer can be
efficiently implemented on GPU hardware as illustrated in
Figure~\ref{fig_lod_octree}-\emph{rigth}.

Finally, before constructing the triangulation from remaining cells
and transition cells, geometrical culling is performed in order to
skip the triangle patch construction which are not visible. Figure
\ref{fig_pipeline} illustrates the overall fully data parallel
pipeline.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.9\textwidth]{figs/pipeline}
  \caption{ Summary our GPU pipeline. Data buffers are
    represented in green and computations in red. Each computation
    retrieves data from a buffer and fills a new one. }
  \label{fig_pipeline} 
\end{figure}
